A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-05 1_intro.tex
add patent notice and implementation link

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.

@@

>>>>

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
\revise{
Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
}{
Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
This paper focusses on the contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with geometry which is narrower than the typical number of perimeters.
}

@@

\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
